---
title: "CheckingFuntion"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CkeckingFuntion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Project 1
## Test funtion
```{r}
library(MATH4793CHUProject1)
```
### Test univariate Normality by theory
```{r}
as.numeric(T4_6$V1)
theoryUnivNormality(x=T4_6$V1)
```

### construct a Q-Q plot
```{r}
getQQplot(T4_6$V1)
```

### find the correlation coefficient of the Q-Q plot
```{r}
corQ(T4_6$V1)
```

### test for bivariate Normality
textbook example
```{r}
x <- cbind(sales, profits)
bivNormality(x, alpha=0.5)
```

dataset example
```{r}
x <- cbind(T4_6$V1, T4_6$V2)
bivNormality(x, alpha=0.5)
```

### test MVN
textbook example
```{r}
x <- cbind(sales, profits)
testMVN(x)
```

dataset example
```{r}
y <- cbind(T4_6$V1, T4_6$V2, T4_6$V3, T4_6$V4, T4_6$V5)
testMVN(y)
```

### Decting Outliers
this one suppose to output  
1. the dotplot for each variable  
2. the scatter plot each pair of variable  (since it is too long, so make is invisible. but could modify through funtion)
3. the list contain standardized_values, generalized_squared_distance, and ouliers (make it invisible)  , just print the outliers out
```{r}
DetectingOutliers(T4_6)$outliers
```




## correlation of boxcox plot
```{r}
boxcox(T4_6$V1)
```

