---
title: "CheckingFuntion"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CkeckingFuntion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Project 1
## Test funtion
```{r}
library(MATH4793CHUProject1)
```
### Test univariate Normality by theory
```{r}
theoryUnivNormality(x=T4_6$V1)
```

### construct a Q-Q plot
```{r}
getQQplot(T4_6$V1)
```

### find the correlation coefficient of the Q-Q plot
```{r}
corQ(T4_6$V1)
```

### test for bivariate Normality
textbook example
```{r}
x <- cbind(sales, profits)
bivNormality(x, alpha=0.5)
```

dataset example
```{r}
x <- cbind(T4_6$V1, T4_6$V2)
bivNormality(x, alpha=0.5)
```

### test MVN
textbook example
```{r}
x <- cbind(sales, profits)
testMVN(x)
```

dataset example
```{r}
y <- cbind(T4_6$V1, T4_6$V2, T4_6$V3, T4_6$V4, T4_6$V5)
testMVN(y)
```

### Decting Outliers
this one suppose to output  
1. the dotplot for each variable  
2. the scatter plot each pair of variable  (since it is too long, so make is invisible. but could modify through funtion)
3. the list contain standardized_values, generalized_squared_distance, and ouliers (make it invisible)  , just print the outliers out
```{r}
DetectingOutliers(T4_6)$outliers
```

### correlation of boxcox plot
```{r}
boxcox(T4_6$V1)
```


# ANSWERING Question
## a) examine marginal normality
Use the Q-Q plot to visualize the marginal normality.  This is because plots of the sample quantile versus the quantile one would expect to observe if the observations actually were normally distributed. When the points lie very nearly along a straight line, the normality assumption remains tenable. Normality is suspect if the points deviate from a straight line. (from textbook)

### independence
Suspect about the Normality because it seem like a lot of dot is away from the line. 
```{r}
getQQplot(T4_6$V1)
```

Use the normal approximation to the sampling distribution of p_hat is departures from an assumed normal distribution for the  characteristic or not.
```{r}
theoryUnivNormality(x=T4_6$V1)
```
The false mean that the data does not show evidence against normality within the scope of these specific checks. 

### support
Suspect about the Normality because it seem like a lot of dot is away from the line.
```{r}
getQQplot(T4_6$V2)
```

Use the normal approximation to the sampling distribution of p_hat is departures from an assumed normal distribution for the  characteristic or not.
```{r}
theoryUnivNormality(x=T4_6$V2)
```
The false mean that the data does not show evidence against normality within the scope of these specific checks. 


### benevolence
This seem like normal distribution, becasue the dot is nearly along a straight line.
```{r}
getQQplot(T4_6$V3)
```

### conformity
This seem like normal distribution, because the dot is nearly along a straight line.
```{r}
getQQplot(T4_6$V4)
```



### leadership
This does not seem like normal distribution, because many dot are away from straight line.
```{r}
getQQplot(T4_6$V5)
```


## b) multivariate normality
```{r}
y <- cbind(T4_6$V1, T4_6$V2, T4_6$V3, T4_6$V4, T4_6$V5)
testMVN(y)
```

## c) transformation that would make it more nearly normal
```{r}

```






